### 2017-10-17 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Continued text. Now on spill point finding and saddle points

		\subsection{Determination of the trap volume}

			\subsubsection{Finding spill and leak points}

@@

>>>>

		\subsection{Determination of the trap volume}
		In the course of this work, several algorithms are developed within the python environment, that in combination enable the automatic recognition and calculation of trap volumes in geological models computed by gemPy. To assign voxels of the model to the trap volume, it is checked whether the following conditions are satisfied by each particular voxel: 
		\begin{enumerate}
				        \item \textbf{Labeled as reservoir formation:} The voxel has been assigned to the target reservoir formation in the lithology block model. This is determined by respective labeling of the input data and the computation conducted by gemPy.
				        \item \textbf{Location in footwall:} The voxel is located on the footwall side of the fault. This condition is applicable to this specific model design, in which entrapment is assumed to occur between the footwall anticlinal enclosure and the normal fault. Due to respective dip of the reservoir formation, full leakage is assumed for the reservoir formation in the hanging wall. A distinction between foot- and hanging wall is easily achievable by using the fault model block that is generated by gemPy. In this fault block, voxels on both sides are assigned respective values for distinction.
				        \item \textbf{Location above spill point horizon:} The voxel is located vertically above the final spill point of the trap. In the algorithm to find this final spill point, it is distinguished between a spill point defined by the folding structure, referred to as anticlinal spill point, and a cross-fault leak point, that depends on the magnitude of displacement and the resulting nature of juxtapositions. Once both of these points have been determined, the higher one is defined to be the final spill point used to determine the maximum fill capacity of the trap. In the case of fault sealing, however, the cross-fault leak point is discarded as irrelevant. The process of finding the decisive spill point is explained below in further detail.
				        \item \textbf{Location inside of closed system:} The voxel is part of a model section inside of the main anticlinal feature. All of the voxels in this section are separated from the borders of the model by voxels that don't meet the conditions above, which primarily means that they are encapsulated by seal voxel laterally and upwards. This condition is applicable  under the assumption, that connection to the borders of the model lead to leakage. A trap is thus defined as a closed system in this model.
		\end{enumerate} 
		REGARD THE RELATIVITY OF THE CONDITIONS AND THE APPROACH TO THIS SPECIFIC MODEL!

			\subsubsection{Finding the final spill point of a trap} %\label{sec:spill_leak_finding}
			Regarding dome-shaped anticlinal structures, it can be observed that, geometrically and mathematically, a spill point is a saddle point of the reservoir top surface in 3D. Two examples for such saddle points are visualized in Figures \ref{fig:saddle_point} and \ref{fig:saddle_point_between_maxima}. The latter one in particular, illustrates well

			\begin{figure}[h]
				%\centering
				\begin{subfigure}{.5\textwidth}
					\centering
					\includegraphics[width=1\linewidth]{Figures/Saddle_point.png}
					\caption{Graph and saddle point of the function $z=x2−y2$.}\label{fig:saddle_point} 
				\end{subfigure}
				\begin{subfigure}{.5\textwidth}
					\centering
					\includegraphics[width=1\linewidth]{Figures/Saddle_Point_between_maxima.png}
					\caption{Saddle point between two maxima.}\label{fig:saddle_point_between_maxima} 
				\end{subfigure}
				\caption{Two examples for saddle points on surfaces of 3D functions (from Wikimedia Commons)}
			\end{figure}

@@

		\subsection{Determination of layer thicknesses}
